### 2017-02-03 chapters/ch2-checkpoint.tex
Validation proof WIP

\subsection{Assumptions}
\begin{itemize}
\item We elect $N$ consensus promoters in every round, we assume the number of
  faulty promoters is $f$ and $N = 3f + 1$.
\item Promoters have the complete history of the previously agreed set of
  transactions.
% \item Single connected component for TrustChain.
% \item No sybil attack % 
\end{itemize}

@@

\item A block of type $\tau$ is a \emph{transaction block}. It is a six-tuple,
  i.e. $$b^\tau_{i,j} = (H(b_{i,j-1}), h_s, h_r, s_s, s_r, m).$$ $h_s$ and $h_r$
  denote the height (the sequence number for when the transaction is made) of
  the sender and receiver respectively. $s_s$ and $s_r$ denote the signature of
  the sender and the receiver respectively.

\item A block of type $\gamma$ is a \emph{checkpoint block}. It is a
  three-tuple, i.e.
  $$b^\gamma_{i,j} = (H(b_{i,j}), H(\mathcal{C}_r), p)$$
  where $\mathcal{C}_r$ is the consensus result in round $r$ and $p \in {0,1}$
  which indicates whether $i$ wish to become a promoter in the following
  consensus round.

\item Given the input $b^\tau_{i,j}$, we define the
  \emph{get-neighbouring-checkpoints function}
  $$C(b^\tau_{i,j}) = (b^\gamma_{i,a}, b^\gamma_{i,b})$$
  where $a = \argmin_{k, k < j, T(b_{i,k}) = \gamma}(j - k)$ and $b =
  \argmin_{k, k > j, T(b_{i,k}) = \gamma}(k - j)$.

\item Given two $\gamma$ transactions, we define \emph{get-piece function}
  $$P(b^\gamma_{i,a}, b^\gamma_{i,b}) = \{b_{i,j} : b_{i,j} \in B_i, a \le j \le
  b\}.$$

\item Given two blockchains and a message, we define the \emph{do-transaction
    function}
  $$X_\tau(B_s, B_r, m) = (B'_s, B'_r)$$
  where $B'_s = \{(H(b_{s,h_s}), h_s + 1, h_r + 1, s_s, s_r, m)\} \cup B_s$,
  $B'_r = \{(H(b_{r, h_r}), h_s + 1, h_r + 1, s_s, s_r, m)\} \cup B_r$, $h_s =
  |B_s|$ and $h_r = |B_r|$.

\item Given a blockchain, we define the \emph{do-checkpoint function}
  $$X_\gamma(B_i, r, p) = \{ (H(b_{i,h}), H(\mathcal{C}_r), p) \}\cup B_i$$ where
  $h = |B_i|$, and $\mathcal{C}_r$ is the latest consensus result.

@@

\item The result of a consensus in round $r$ is a set of two-tuple of
  checkpoints. Namely, $\mathcal{C}_r = \{ (b^\gamma_{i,a}, b^\gamma_{i,b}) : a
  < b, \text{agreed by the promoters}\}$.
\end{itemize}

@@

\subsection{Setup phase}
We begin in the state where $\mathcal{C}_{r-1}$ has just been agreed but has not
been disseminated yet.
\begin{lemma}
  Nodes in the network can always verify the validity of the consensus result.
\end{lemma}
\begin{proof}
\end{proof}

@@

\subsection{Consensus phase}

@@

\subsection{Breadth first search}

\subsection{Random sampling}

>>>>

\subsection{Assumptions}
\begin{itemize}
\item Asynchronous network
\item Private and authenticated channel
\item We elect $N$ consensus promoters in every round, we assume the number of
  faulty promoters is $f$ and $N = 3f + 1$.
\item Promoters have the complete history of the previously agreed set of
  transactions (TX).
% \item Single connected component for TrustChain.
% \item No sybil attack % 
\end{itemize}

@@

\item A block of type $\tau$ is a \emph{transaction block} or \emph{TX block}.
  It is a six-tuple, i.e. $$b^\tau_{i,j} = (H(b_{i,j-1}), h_s, h_r, s_s, s_r,
  m).$$ $h_s$ and $h_r$ denote the height (the sequence number for when the TX
  is made) of the sender and receiver respectively. $s_s$ and $s_r$ denote the
  signature of the sender and the receiver respectively. $i = \{s, r\}$ and $j =
  \{h_s, h_r\}$ and we call the block a sender block or a receiver block
  respectively.

\item Given two TX blocks $b^\tau_{i,j}$ and $b^\tau_{i',j'}$, but $i \neq i'$.
  If $h_s = h'_s$, $h_r = h'_r$, $m = m'$ and the signatures are valid, then we
  call them a \emph{pair}.

\item If there exist two TX blocks $b^\tau_{i,j}$ and $b^\tau_{i',j'}$, where
  $s_s$ and $s_s'$ is created by the same public key and $h_s = h_s'$ but $i
  \neq i'$, then we call this a \emph{fork}.

\item A TX block has two \emph{inputs} blocks, to retrieve the input we define
  the \emph{get-tx-input function} $I^\tau$. Let the pair of $b^\tau_{i,j}$ be
  $b^\tau_{i',j'}$, then
  $$I^\tau(b^\tau_{i,j}) = (b_{i, j-1}, b_{i', j'-1}).$$

\item A block of type $\gamma$ is a \emph{checkpoint block} or \emph{CP block}.
  It is a three-tuple, i.e.
  $$b^\gamma_{i,j} = (H(b_{i,j}), H(\mathcal{C}_r), p)$$
  where $\mathcal{C}_r$ is the consensus result in round $r$ and $p \in {0,1}$
  which indicates whether $i$ wish to become a promoter in the following
  consensus round.

\item A CP block has one input, we define the \emph{get-cp-input
    function} $$I^\gamma(b^\gamma_{i,j}) = b_{i,j-1}.$$

\item Given the input $b^\tau_{i,j}$, we define the
  \emph{get-nearest-cp function}
  $$C(b^\tau_{i,j}) = (b^\gamma_{i,a}, b^\gamma_{i,b})$$
  where $a = \argmin_{k, k < j, T(b_{i,k}) = \gamma}(j - k)$ and $b =
  \argmin_{k, k > j, T(b_{i,k}) = \gamma}(k - j)$.

\item Given two $\gamma$ blocks, we define \emph{get-piece function}
  $$P(b^\gamma_{i,a}, b^\gamma_{i,b}) = \{b_{i,j} : b_{i,j} \in B_i, a \le j \le
  b\}.$$

\item Given two blockchains and a message, we define the \emph{do-tx-function}
  $$X_\tau(B_s, B_r, m) = (B'_s, B'_r)$$
  where $B'_s = \{(H(b_{s,h_s}), h_s + 1, h_r + 1, s_s, s_r, m)\} \cup B_s$,
  $B'_r = \{(H(b_{r, h_r}), h_s + 1, h_r + 1, s_s, s_r, m)\} \cup B_r$, $h_s =
  |B_s|$ and $h_r = |B_r|$.

\item Given a blockchain, we define the \emph{do-cp function}
  $$X_\gamma(B_i, r, p) = \{ (H(b_{i,h}), H(\mathcal{C}_r), p) \}\cup B_i$$ where
  $h = |B_i|$, and $\mathcal{C}_r$ is the latest consensus result.

@@

\item The result of a consensus in round $r$ is a set of two-tuple of CP.
  Namely, $\mathcal{C}_r = \{ (b^\gamma_{i,a}, b^\gamma_{i,b}) : a < b,
  \text{agreed by the promoters}\}$.
\end{itemize}

@@

\subsection{Setup phase}
We begin in the state where $\mathcal{C}_{r-1}$ has just been agreed but has not
been disseminated yet. The promoters

\begin{lemma}
  If a node sees a valid $\mathcal{C}_r$ and another node sees a valid
  $\mathcal{C}'_r$, then $\mathcal{C}_r = \mathcal{C}'_r$.
\end{lemma}
\begin{proof}
\end{proof}

@@

\subsection{Consensus phase}
We need an atomic broadcast algorithm for the consensus phase. We use a similar
but simplified construction as~\cite{miller2016honey}, where atomic broadcast is
constructed from the reliable broadcast\footnote{Reliable broadcast solves the
  Byzantine generals problem.}~\cite{bracha1984asynchronous} and asynchronous
common subset (ACS). The ACS protocol requires a binary Byzantine agreement
protocol, and for that it needs a trusted dealer to distributed the secret
shares. Promoters can check whether the secret shares are valid, but they cannot
prevent the dealer from disclosing the secrets.

There techniques that uses no dealers. First is to use
PBFT~\cite{castro1999practical}, but we must change our asynchronous assumption
into the weak synchrony assumption. Second is to use an inefficient binary
Byzantine agreement protocol where its message complexity is $O(N^3)$ rather
than $O(N^2)$ and becomes a bottleneck.

Suppose we use a dealer, what is the effect to the algorithm if the dealer is
malicious?

@@

\subsection{Depth first search}
\begin{algorithmic}
\State{$bs = \emptyset$}

\Procedure{reverse-dfs}{$G, b$}
\State {$bs \gets {b} \cup bs$}
\If{$t = \text{genesis}$}
    \State \textbf{return} $1$
\EndIf
\ForAll{$d \in I(b)$}
\If{\Call{valid}{$d$} = 0}
   \State {\textbf{return} 0}
\EndIf
\EndFor

\State {\textbf{return} 1}
\EndProcedure
\end{algorithmic}

\begin{algorithmic}
\Procedure{valid}{$b, bs$}

\State $(b^\gamma_a, b^\gamma_b) = C(b)$
\State $p = P(b^\gamma_a, b^\gamma_b)$
\If{$(b^\gamma_a, b^\gamma_b)$ is in a consensus result}
  \If{$p$ is a valid chain}
    \If{$b$ does not have a \emph{fork} in $bs$}
      \State {\textbf{return} $1$}
    \EndIf
  \EndIf
\EndIf

\State \textbf{return} $0$
\EndProcedure
\end{algorithmic}

\begin{lemma}
  The \verb!reverse-dfs! algorithm traverses all nodes that may have an effect
  on block $b$.
\end{lemma}
\begin{proof}
  Recall that the TrustChain is a DAG, which always has a topological ordering.
  That is, for every edge $(b', b)$, $b'$ comes before $b$ in the ordering, and
  nodes before $b$ are its ancestors. If we reverse all the edges, then $b'$
  comes after $b$ in the ordering, and nodes before $b$ are its descendents.

  \verb!reverse-dfs! is essentially running DFS with all the edges reversed. If
  the DFS outputs the visited nodes in reverse postordering, then the output is
  in topological order and contains all of $b$'s original ancestors. Due to the
  hash pointers, only the ancestors can have an effect on $b$.
\end{proof}

\begin{lemma}
  \verb!verify!...
\end{lemma}
\subsection{Random sampling}
